#model is not working yet

```{r echo=FALSE}
# Step 1: Load the necessary libraries
library(forecast)
```
```{r echo=FALSE}
load("dataframe.RData")
```
```{r echo=FALSE}
divorciosDFdepar <- divorcios_anio_mes_departamento
```


```{r echo=FALSE}
str(divorciosDFdepar)
head(divorciosDFdepar)
```


# Step 3: Explore the data
# Plot the time series data
```{r echo=FALSE}
plot(divorciosDFdepar$date, divorciosDFdepar$divorces, type = 'l', xlab = 'Mes', ylab = 'Divorcios', main = 'Divorces a través del tiempo')
```

# Step 4: Account for Pandemic Impact
# Create a binary variable indicating the presence of the pandemic
```{r echo=FALSE}
divorciosDFdepar$pandemic <- ifelse(divorciosDFdepar$date >= as.Date('Marzo 2021'), 1, 0)
```
# Step 5: Model Selection and Estimation
# Fit an ARIMA model with exogenous variable (pandemic)
```{r echo=FALSE}
model <- auto.arima(divorciosDFdepar$divorces, xreg = divorciosDFdepar$pandemic)
```
# Step 6: Model Evaluation
# Split the data into training and testing sets
```{r echo=FALSE}

train_data <- window(divorciosDFdepar$divorces, end = c(year(divorciosDFdepar$date)[length(divorciosDFdepar$date)-12], month(divorciosDFdepar$date)[length(data$date)-12]))
test_data <- window(divorciosDFdepar$divorces, start = c(year(divorciosDFdepar$date)[length(divorciosDFdepar$date)-11], month(divorciosDFdepar$date)[length(divorciosDFdepar$date)-11]))
# Fit the ARIMA model to the training data
model <- auto.arima(train_data, xreg = window(divorciosDFdepar$pandemic, end = length(train_data)))
# Generate forecasts for the testing set
forecasts <- forecast(model, xreg = window(divorciosDFdepar$pandemic, start = length(train_data) + 1))
# Evaluate the model performance
accuracy(forecasts, test_data)
```

# Step 7: Forecasting
# Fit the ARIMA model to the entire data
```{r echo=FALSE}
model <- auto.arima(divorciosDFdepar$divorces, xreg = divorciosDFdepar$pandemic)
# Generate forecasts for the desired time horizon
future_forecasts <- forecast(model, xreg = rep(1, 12))  # Forecasting for the next 12 months
# Print the forecasted values
print(future_forecasts)
```